R Notebook

### 2021-08-16 Paper_Figure_code.Rmd
Fig5

p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"BPRNA") +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

@@

melt_GSE107011_BPRNA_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.04)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.038, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.033, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.018, y = 0.0275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)

>>>>

p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"BPRNA") +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, limits = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

@@

melt_GSE107011_BPRNA_EpiDISH[[6]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.08)) +
  scale_y_continuous(name = NULL, limits = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.038, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.033, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.018, y = 0.0275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)
